\cvsection{Experience}

\begin{cventries}
  \cventry
  {Programming Lead} % Job title
  {FIRST Tech Challenge --- Robotics Competition} % Organization
  {San Jose, CA} % Location
  {Sept. 2016 - May 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Refined the pure-pursuit path following algorithm to make better use of holonomic drivetrains; quicker (autonomous) navigation between waypoints made it possible for robots to score more points during the fixed 30-second game period.}
      \item {Established a CAD-first workflow within a 15-member team, teaching members to fully design robot mechanisms in SolidWorks; sped up the prototype/build cycle and helped team take full advantage of 3D printing.}
      \item {Delegated tasks to a 3-member programming subteam using GitHub.}
      \item {Earned the Control Award at World Championships for excellent robot performance because of well-tested code and innovative computer vision algorithms.}
    \end{cvitems}
  }

  \cventry
  {Frontend Developer, Graphic Designer Intern} % Job title
  {Sleekfin --- Real Estate Startup} % Organization
  {San Jose, CA} % Location
  {May 2020 - Aug. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created a full mobile app mockup with 30+ screens in Adobe XD from verbal descriptions of desired functionality.}
      \item {Developed React Native components for user input; migrated existing codebase to use these new components, unifying the app's design langauge.}
    \end{cvitems}
  }

  \cventry
  {Co-Founder, Head of Curriculum} % Job title
  {Hack on Track --- STEM Education Nonprofit} % Organization
  {San Jose, CA} % Location
  {June 2018 - May 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Taught weekly coding workshops at community centers and low socioeconomic status schools covering SCRATCH, Python, and JavaScript using self-written lesson plans; reached rougly 10--20 new students each session.}
    \end{cvitems}
  }
\end{cventries}
