\cvsection{Projects}

\begin{cventries}
  \cventry
  {React, GraphQL, PostgreSQL, Azure Functions} % Languages
  {KiloDoc --- Collaborative Typesetting Web App} % Project
  {} % Empty location
  {Apr. 2020 - PRESENT} % Empty date
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Provisioned a full-stack web app consisting of static React code and a GraphQL API running on Azure Functions connected to a PostgreSQL database.}
      \item {Optimized the performance of infinitely-scrolling cloud documents by designing a tree-like storage format and dynamically loading/unloading subtrees based on browser viewport.}
      \item {Wrote certain SQL queries by hand (instead of using an ORM) to speed up performance-critical tasks and enable complex operations like full-text search within a document subtree.}
      \item {Solved the tricky issue of PDF generation by using headless Chromium instances controlled by Puppeteer, consuming an Azure Service Bus Queue and writing to Azure Blob Storage.}
    \end{cvitems}
  }

  \cventry
  {Java} % Languages
  {Foxtrot --- Rapid 2D Spline Generation GUI} % Project
  {} % Empty location
  {Oct. 2019 - Mar. 2020} % Empty date
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Built a 2D interface using Java Swing for editing splines by drag-and-dropping anchors; supports viewport x/y translation and zoom.}
      \item {Utilized by robotics team to rapidly create and test autonomous robot paths.}
      \item {Developed custom file format based on JSON that stored the minimum representation of paths; format also contained an array of coordinates and curvatures along the path to aid the robot's path following algorithm.}
    \end{cvitems}
  }

  \cventry
  {Python, Flask, T-SQL} % Languages
  {PALS --- Robotics Tournament Scouting Platform} % Project
  {} % Empty location
  {Nov. 2018 - Apr. 2019} % Empty date
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Created an online tournament scoring platform on which specifications for each season's robot game could be registered; platform uses game specifications to create scouting forms where each input (checkbox, numeric, etc.) is assigned a point value; platform aggregates form submissions across a tournament to display bar graphs showing team rankings and report each team's strengths/weaknesses.}
    \end{cvitems}
  }
\end{cventries}
